### 2020-08-20 ReadMe.rmd
test
update readme

The goal of this repository is to allow future users to rerun the analysis and build on it if necessary, but also to facilitate the writing of the publication that will come out of the thesis by enforcing good reproducibility practices early on in the publication process.

@@

*Disclaimer 1: Although all the code for the thesis is archived here, parts of the analysis are not reproducible, as some of the data used is not in open access.*

*Disclaimer 2: The simulation code is designed to be paralellized on a large linux machine (not an HPC environment) of the type [Arbutus Compute Cloud](https://docs.computecanada.ca/wiki/Cloud_resources) from Compute Canada. However, the final steps (analysis, figure making) can be ran on computer of a much more modest size.*

@@

Once the image is downloaded, you can run it in a container. Multiple options are possible. For simulation code, it is important to increase the access to shared memory for the container with the option `--shm-size` (give as much as you can afford, I usually use `50G`).

  - **Run docker image interactively** (`docker run [options] vlucet/land_con_monteregie:3.6.2-1 /bin/bash && cd ~/land_con_monteregie`), executing a command that starts bash and move to the repo directory (`/bin/bash && cd ~/land_con_monteregie`), with options to run an interactive terminal (`-it`) with authentification disabled (` DISABLE_AUTH=true`).

```{}
docker run -it -u rstudio -e DISABLE_AUTH=true vlucet/land_con_monteregie:3.6.2-1 /bin/bash && cd ~/land_con_monteregie
```

@@

```{}
./landcon.sh -g
```

@@

The first steps cover data preparation and Land Use change modeling (see figure below):

>>>>

The goal of this repository is to allow future users to rerun the analysis and build on it if necessary, but also to enforce good reproducibility practices as early as possible in the publication process.

@@

*Disclaimer: Although all the code for the thesis is archived here, parts of the analysis are not reproducible, as some of the data used is not in open access. The simulation code is designed to be paralellized on a remote linux machine (not an HPC or local environment) of the type [Arbutus Compute Cloud](https://docs.computecanada.ca/wiki/Cloud_resources) from Compute Canada. However, the final steps (analysis, figure making) can be ran on computer of a much more modest size.*

@@

Once the image is downloaded, you can run it in a container. **Two options are available**. For simulation code, it is important to increase the access to shared memory for the container with the option `--shm-size` (give as much as you can afford, I usually use `50G`).

  - **Run docker image interactively *(recommended)* ** (`docker run [options] vlucet/land_con_monteregie:3.6.2-1 /bin/bash && cd ~/land_con_monteregie`), executing a command that starts bash and move to the repo directory (`/bin/bash && cd ~/land_con_monteregie`), with options to run an interactive terminal (`-it`) with authentification disabled (` DISABLE_AUTH=true`).

```{}
docker run -it -u rstudio -e DISABLE_AUTH=true vlucet/land_con_monteregie:3.6.2-1 \
  /bin/bash && cd ~/land_con_monteregie
```

@@

```{}
./landcon.sh figs
```

@@

The utility has multiple options, each one to run a separate step of the analysis. The first steps cover data preparation and Land Use change modeling (see figure below):
